% My Resume
\documentclass[a4paper]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{textcomp}
\usepackage{varwidth}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{enumitem}

\setlist[itemize]{itemsep=0pt, topsep=0pt}
\textheight=10in
\pagestyle{empty}
\raggedright
\usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}
\usepackage[hidelinks]{hyperref}
\hypersetup{
colorlinks=true, urlcolor=blue
}
\urlstyle{same}
%\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
\vspace*{-9pt}
\begin{verse}
\textbf{#1}   #2
\end{verse}
}

\newcommand{\lineunder} {
\vspace*{-8pt} \\
\hspace*{-18pt} \hrulefill \\
}

% \newcommand{\header} [1] {
% {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
% \vspace*{-6pt} \lineunder
% }

\newcommand{\header}[1]{%
{\hspace*{-18pt}\vspace*{6pt} \textsc{\textbf{\Large{#1}}}}%
\vspace*{-6pt} \lineunder
}
\newcommand{\employer} [3] {
{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
\vspace*{-10pt}
\begin{center}
{\Huge \scshape {#1}}\\
#2 \\ #3
\end{center}
\vspace*{-8pt}
}

\newenvironment{achievements}{
\begin{list}
{$\bullet$}{\topsep{0pt} \itemsep{-2pt}}}{\vspace*{4pt}
\end{list}
}

\newcommand{\schoolwithcourses} [4] {
\textbf{#1} #2 $\bullet$ #3\\
#4 \\
\vspace*{5pt}
}

\newcommand{\school} [4] {
\textbf{#1} #2 $\bullet$ #3\\
#4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\vspace*{-40pt}

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
{\Huge \scshape \textbf {Swarnim Barapatre}}\\
Kalyani Nagar, Pune $\cdot$ swarnim335@gmail.com $\cdot$ 8149833469 $\cdot$ \href{https://github.com/swarnimcodes/}{GitHub} \\ % $\cdot$ \href{https://smarniw.xyz}{smarniw.xyz} \\
\end{center}

%==== Education ====%
\header{Education}

{\textbf{BITS, Pilani}}\hfill May 2019 -- Aug 2024\\
Dual Degree: BE Chemical Engineering + MSc Biological Sciences %\hfill May 2019 - Aug 2024\\

\vspace{4mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}
\textbf{Software Engineer, R\&D Department, Mastersoft} \hfill Aug 2023 -- Jun 2024 \\
% \textbf{Mastersoft} \hfill Nagpur\\
% \textit{Software Development Engineer, R\&D Department} \hfill Aug 2023 - June 2024\\
\vspace{-1mm}
\begin{itemize}
    % \item Developed the Employee Productivity Measurement System from ground-up, eliminating the
    % need for \href{https://desktime.com/}{DeskTime} subscriptions. \\
    % \item Enhanced educational practices within the ERP by engineering a suite of OpenAI powered APIs. \\
    % \item Automated the identification and mitigation of security vulnerabilites across company websites by
    % developing a Website Vulnerability Identificatier.
    % \item Automated operations for Azure Blob Storage and Microsoft SQL Server, resulting in reduction 
    % in operation's completion time, human effort and error surface area. \\
    % \item Resolved critical Linux server issues, reducing downtime and mitigating data loss risks. \\

    \item Designed system architecture and developed a high-traffic product,
    as part of a three person team. \\
    \item Built asynchronous and scalable backend systems with FastAPI. \\
    \item Researched and developed backend systems in Go to assess advantages
    over currently used backend technologies in the organization. \\
    \item Developed internal developer tools for the database and software development teams,
    cutting down hours of manual effort and reducing error surface. \\
    \item Resolved critical Linux Server issues, 
    preventing significant downtime and data loss. \\

\end{itemize}

% \vspace{2mm}

\header{Skills}
\vspace{1mm}

\begin{tabular}{V{5cm} @{\hskip 0.6cm} V{12cm}}
% Skilled: & Python, Flask, FastAPI, Linux Servers \\
% Intermediate: & Powershell, Bash Scripting, Git, Vim, \LaTeX, Nginx, MS-SQL, Go \\
% Beginner: & C, C++, Java, Pascal, DSA \\
\textbf{Programming Languages:} & Python, Go, Powershell, Bash, C, Pascal \\

\textbf{Web Frameworks:} & 
    \href{https://github.com/pallets/flask}{Flask},
    \href{https://github.com/tiangolo/fastapi}{FastAPI},
    \href{https://pkg.go.dev/net/http}{net/http},
    \href{https://github.com/go-chi/chi}{Chi} \\

\textbf{Databases:} & Microsoft SQL Server, SQLite, MongoDB \\

\textbf{Tools/Technologies:} & Linux, Git, Postman, Vim, Nginx, \LaTeX{} \\

\end{tabular}

\vspace{4mm}

% ===== Projects Section ======

\header{Projects}
\vspace{1mm}

{\textbf{Employee Performance System}}\hfill \href{https://github.com/swarnimcodes/employee-performance}{Git}\\
\begin{itemize} 
    \item Designed and developed a multi-tenant
    application for streamlined productivity
    tracking. \\
    \item Reduced annual costs by \textbf{Rs 53 Lakhs} by eliminating 
    reliance on \href{https://desktime.com/}{external services}. \\
    \item Facilitated confident remote talent recruitment through accurate productivity metrics.\\ 
    \item Implemented features such as interventionless atomic app updates,
    a live-updating configuration system, and encrypted activity logs. \\
    \item Utilized a diverse tech stack including Python, Powershell, Pascal, and Win32 APIs. \\
\end{itemize}
\vspace*{2mm}

{\textbf{MS-SQL Suite of Tools }}\hfill \href{https://github.com/swarnimcodes/Sequel}{Git}\\
\begin{itemize} %\itemsep 0pt \topsep 0pt
    \item Crafted a suite of tools for the Microsoft SQL Server, achieveing
    85\% time reduction in SQL task flows. \\
    \item Developed a tool to optimize memory consumption by identifying memory leaks in the database. \\
    \item Developed tools to compare and contrast database stored procedures and SQL functions,
    visualizing differences via automated reports and generating alter scripts to synchronize databases. \\
    \item Used Python along with libraries such as difflib, sqlparse, and pyodbc. \\
\end{itemize}
\vspace*{2mm}

{\textbf{Persistent Queue System}}\hfill \href{https://github.com/swarnimcodes/kafkaesqueue}{Git}\\
\begin{itemize} 
    \item Developed a resilient queue system to automate time-intensive tasks,
    ensuring FIFO completion and allowing for remote task addition. \\
    \item Implemented persistence to maintain queue integrity during system crashes. \\
    \item Reduced queue completion times by introducing optional parallel processing. \\
    \item Used FastAPI as the backend framework along with Pydantic for data validation. \\
\end{itemize}

\vspace*{2mm}

{\textbf{OpenAI APIs}}\hfill \href{https://github.com/swarnimcodes/openai-gen-co-and-qp}{Git}\\
\begin{itemize} 
    \item Developed multiple APIs leveraging the power of OpenAI to introduce
    innovative features.
    \item Implemented AI solutions for rubrik-based grading, SQL-driven report generation,
    question paper and course outcome generation to name a few. \\
    \item Utilized Flask and FastAPI with MS-SQL as the database. \\
\end{itemize}
\vspace*{2mm}

% {\textbf{Go API Blueprint} [Personal]\hfill \href{https://github.com/swarnimcodes/apigo}{Git}}
% \begin{itemize}
%     \item Developed a comprehensive API server blueprint using the standard \texttt{net/http} library in Go.
%     % \item Allows you to spin up a web-server with sane defaults, built-in authorization, 
%     % elegant middleware usage interface, database connectivity, and get going with your project
%     \item Implemented essential features: authorization, middleware interface, and database connectivity.
%     \item Designed for facilitating rapid project setup.
% \end{itemize}
% \vspace{2mm}

{\textbf{Other Projects}\hfill \href{https://github.com/swarnimcodes/}{Git}} \\
Other projects include: 
\href{https://github.com/swarnimcodes/website}{personal website using golang + server side rendering},
\href{https://github.com/swarnimcodes/apigo}{golang API blueprint},
% \href{https://github.com/swarnimcodes/kafkaesqueue}{a persistent queue system},
\href{https://github.com/swarnimcodes/website-security-checker}{website vulnerability identifier},
API health monitoring system, 
automation tools for Azure Blob Storage, etc.
\vspace{2mm}


\vspace{2mm}
%==== Extra Curriculars ====%
\header{Extra Curriculars}
\vspace{1mm}

\textbf{Swimming}: Represented Maharashtra in National Championships. Multiple State Level Gold Medalist.

\end{document}
